### 2020-10-25 ChapterConclusion/chapterConclusion.tex
Fixed: Typo in Conclusion

The overhead of boundary objects graph (Fig. \ref{fig_PerfOverheadColumn}) contains a lot of noise and the results are close to the error margin of the fitted line (~0.5ms for the number of objects involved). However, it appears as though there is a positive trend between increasing nodes and increasing overhead, which converges at 8 servers. It is also not clear what the exact relationship is between boundary objects and frame-time as the data for 3 and more servers are indicative of a linear relationship, however, the data for 2 servers suggests an exponential relationship, but based only on the point at 2500 objects and this may be a result of noisy data. More data is required to draw more concrete conclusion, such as a greater number of iterations or experiments that have greater numbers of objects per server when more servers are used.

>>>>

The overhead of boundary objects graph (Fig. \ref{fig_PerfOverheadColumn}) contains a lot of noise and the results are close to the error margin of the fitted line (~0.5ms for the number of objects involved). However, it appears as though there is a positive trend between increasing nodes and increasing overhead, which converges at 8 servers. It is also not clear what the exact relationship is between boundary objects and frame-time as the data for 3 and more servers are indicative of a linear relationship, however, the data for 2 servers suggests an exponential relationship, but based only on the point at 2500 objects and this may be a result of noisy data. More data is required to draw a more concrete conclusion, such as a greater number of iterations or experiments that have greater numbers of objects per server when more servers are used.
